%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Nathan T. Hatch} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
\address{\href{https://nhatch.github.io}{https://nhatch.github.io} \\ Seattle, WA, USA \\
         \href{mailto:nhatch2REMOVE_THIS_PART@uw.edu}{nhatch2@uw.edu} \\ +1 970-297-8081 }

\begin{document}

\begin{rSection}{Education}

{\bf University of Washington, Seattle} \hfill {January 2020 - expected 2023} \\
Ph.D. in Computer Science \& Engineering; Advisor: Dr. Byron Boots

{\bf Georgia Institute of Technology} \hfill {August 2017 - December 2019} \\
Ph.D. student in Machine Learning; Advisor: Dr. Byron Boots

{\bf University of Chicago} \hfill {September 2010 - June 2014} \\
B.S. in Mathematics with honors \\
B.S. in Computer Science with honors

\end{rSection}

\begin{rSection}{Publications}

A. Shaban, C. Cheng, {\bf N. Hatch}, and B. Boots. ``Truncated Back-Propagation for Bilevel Optimization.''
{\em Proceedings of the 22nd International Conference on Artificial Intelligence and Statistics (AISTATS 2019).}
\sref{http://proceedings.mlr.press/v89/shaban19a.html}.

{\bf N. Hatch}. ``Group Theory: An Introduction and an Application.'' {\em University of Chicago VIGRE REU}; 2011.
\href{http://www.math.uchicago.edu/~may/VIGRE/VIGRE2011/REUPapers/Hatch.pdf}{http://www.math.uchicago.edu/$\sim$may/VIGRE/VIGRE2011/REUPapers/Hatch.pdf}.

\end{rSection}

\begin{rSection}{Unpublished Research Projects}

\begin{rProject}{High-speed obstacle avoidance for autonomous vehicles}{June 2019 - present}
\item Adapted model-predictive path-integral control to a goal-seeking navigation and mapping stack
\item Sped up the LIDAR processing pipeline to 10Hz to support 3m/s vehicle velocities
\item Designed and ran three days of experiments on Clearpath Jackal robots with Ouster LIDAR sensors
\end{rProject}

\begin{rProject}{Curriculum-based learning for bipedal locomotion over rough terrain}{May 2018 - May 2019}
\item Extensively studied prior work in locomotion and summarized it in a two-hour lab presentation
\item Invented an algorithm to learn a real-time, dynamic bipedal locomotion controller
\item Tested the algorithm on challenging ``stepping stone'' environments using the DART simulator
\end{rProject}

\end{rSection}

\begin{rSection}{Personal Projects}
  \begin{tabular}{ll}
    \sref{https://github.com/nhatch/slam} & Factor graph SLAM implemented from scratch \\
    \sref{https://github.com/nhatch/rrt} & RRT motion planning implemented from scratch \\
    \sref{https://github.com/nhatch/ilqr} & Iterative LQR control implemented from scratch \\
    \sref{https://github.com/nhatch/mcts} & A (pretty good) AI for Mancala using Monte Carlo tree search \\
    \sref{https://github.com/nhatch/mnist} & Multilayer perceptron for MNIST digit recognition from scratch \\
    % Removed to help pagebreaks line up with section breaks
    %\sref{https://github.com/nhatch/casia} & Convolutional network for CASIA Chinese characters using Keras
  \end{tabular}
\end{rSection}

\begin{rSection}{Work Experience}
\begin{rSubsection}{Full-stack software engineer}{ June 2014 - July 2017}{ eSpark Learning}{ Chicago, IL}
\item Led the annual iOS app release, removing 300ms tap delay and rewriting the video uploader
\item Increased sales pipeline by 25\% by integrating our product with Airwatch
\item Improved academic fidelity metric from 80\% to 87\% by refining our app deployment system
\item Implemented Apple's ``Device Assignment'' protocol, making our MDM first-to-market (solo project)
\item Conducted $\sim$20 interviews and code challenge reviews for recruiting
\end{rSubsection}
\begin{rSubsection}{ chiTCP developer}{ October 2013 - June 2014}{ Dept. Computer Science, University of Chicago}{ Chicago, IL}
\item Implemented a TCP-over-TCP daemon for use in Borja Sotomayor's networks class
\end{rSubsection}
\begin{rSubsection}{ Software intern}{ June - August 2013}{ Mission Street Manufacturing}{ Santa Barbara, CA}
\item Developed prototype front- and back-end software for consumer-friendly 3D printing
\end{rSubsection}
\end{rSection}

\begin{rSection}{Class Projects}
S. Foley, N. Hatch, and A. Beedu. {\em A Global Optimal Solution to Non-Minimal Relative Pose Estimation.} ECE 8823 Convex Optimization; Spring 2019. \\
PDF: \sref{https://nhatch.github.io/files/FoleyHatchBeeduNotes.pdf}

N. Hatch and E. Wijmans. {\em Probabilistic Graphical Modeling of Data-Dependent Annotator Accuracy for Active Learning.} CS 8803 Probabilistic Graphical Models; Spring 2018. \\
Paper: \sref{https://nhatch.github.io/files/Hatch\_Wijmans\_final\_report.pdf} \\
Slides: \sref{https://nhatch.github.io/files/Hatch\_Wijmans\_presentation\_slides\_v2.pdf}

N. Hatch, A. Sundaresan, M. Dutreix, R. Kuppan, and P. Pattanashetty. {\em Google Landmark Recognition and Retrieval Challenges.} ECE 6254 Statistical Machine Learning; Spring 2018. \\
Paper: \sref{https://nhatch.github.io/files/landmarks\_report.pdf} \\
Poster: \sref{https://nhatch.github.io/files/landmarks\_poster.pdf}

N. Hatch. {\em Unsupervised Curriculum Learning for Image Clustering.} CS 7643 Deep Learning; Fall 2017. \\
Poster: \sref{https://nhatch.github.io/files/image-clustering.pdf}

Other graduate-level classes (exam-based): Linear Systems, Theoretical Statistics, Machine Learning Theory, Mathematical Foundations of Machine Learning
\end{rSection}

\begin{rSection}{Awards and Honors}
Georgia Institute of Technology, Presidential Fellowship \hfill 2017 – 2019 \\
University of Chicago, Dean's List \hfill 2010 – 2014 \\
University of Chicago, University Scholarship \hfill 2010 – 2014 \\
University of Chicago, National Merit Scholarship \hfill 2010 – 2014 \\
University of Chicago, Student Marshal \hfill 2013 \\
Phi Beta Kappa \hfill 2013 \\
University of Chicago, Fulton Prize for Orchestral Excellence \hfill 2012
\end{rSection}

\begin{rSection}{Teaching Experience}
\begin{rSubsection}{Teaching assistant, undergraduate machine learning}{Fall 2019}{College of Computing, Georgia Tech}{Atlanta, GA}
\item Graded homework, held weekly office hours, answered Piazza questions, and wrote the final project
\end{rSubsection}
\begin{rSubsection}{Volunteer tutor}{ January 2015 - May 2017}{ Insight Tutoring}{ Chicago, IL}
\item Reviewed homework and class material for three economically disadvantaged sixth-grade students
\item Periodically revisited old material for spaced retrieval practice
\end{rSubsection}
\begin{rSubsection}{Homework grader, graduate discrete mathematics}{ October - December 2012}{ Dept. Computer Science, U. of Chicago}{ Chicago, IL}
\item Graded twice-weekly problem sets for Laszlo Babai's graduate-level class
\end{rSubsection}
\begin{rSubsection}{ SESAME teaching assistant}{ July 2012}{ Dept. Mathematics, U. of Chicago}{ Chicago, IL}
\item Assisted teaching a class for middle school math teachers on ``problem-based learning''
\end{rSubsection}
\begin{rSubsection}{ Young Scholars Program Counselor}{ June - July 2012}{ Dept. Mathematics, U. of Chicago}{ Chicago, IL}
\item Tutored four 9th/10th-grade math students in an advanced summer math program
\item Assisted teaching a class in basic computer programming
\item Gave weekly reports on student progress, including helping to write a diagnostic exam
\end{rSubsection}
\end{rSection}

\begin{rSection}{Professional Service}
\begin{rSubsection}{Co-creator of Machine Learning Student Seminar}{Fall 2019}{Georgia Tech Machine Learning (ML@GT)}{Atlanta, GA}
\item With one co-organizer, started a new seminar with eight presentations to a 25-student audience
\item Invited presenters, including five faculty lightning talks
\item Organized catering, room reservations, and publicity
\end{rSubsection}
\end{rSection}

\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, C++, Javascript/HTML/CSS, Ruby \\
Robotics and Simulation Software & ROS, Gazebo, DART \\
Deep Learning Frameworks & PyTorch, TensorFlow \\
Tools & Git, Vim, LaTeX \\
Foreign Languages & Spanish
\end{tabular}
\end{rSection}

\begin{rSection}{Hobbies}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Places visited & Spain, United Kingdom, Japan, Argentina, Brazil, Taiwan, Hong Kong,\\
& Singapore, China, Peru, South Africa, Namibia, Botswana, Zimbabwe, Turkey \\
Other interests &  viola performance, rock climbing, go (the board game)
\end{tabular}
\end{rSection}

\end{document}
